Formalizing the Kolmogorov extension Theorem in Lean

### 2024-07-05 Manuscript/proof_outline.tex

\subsection{Formulating the result}
Before we can state the result, we begin with some mathematical notions. We start off from metric spaces, but quickly introduce projective families of measures. In all definitions, $\alpha$ will be some set (or type, since {\tt Lean} is a dependently typed language, \leanline{α : Type _}).

@@

In contrast to statements already part of \leanline{mathlib}, in the
sequel we \leanlinecolor{highlight} definitions and statements which
are part of our own code. In the formalization of the above, we use
\leanline{variable {ι : Type _} {α: ι → Type _}}, which fixes the
index set $\iota$ and all spaces $\alpha_t, t\in\iota$ as global
variables.  In Lean, the product space is then \leanline{∀ j : ι, α j}
and the product over a finite subset \leanline{J} of \leanline{ι} is \leanline{∀ j : J, α
  j}.

>>>>

\subsection{Formulating the result}
Before we can state the result, we begin with some mathematical notions. We start off from metric spaces, but quickly introduce projective families of measures. In all definitions, $\alpha$ will be some set (or type, since {\tt Lean} is a dependently typed language, \leanline{α : Type*}).

@@

In contrast to statements already part of \leanline{mathlib}, in the
sequel we \leanlinecolor{highlight} definitions and statements which
are part of our own code. In the formalization of the above, we use
\leanline{variable {ι : Type*} {α: ι → Type*}}, which fixes the
index set $\iota$ and all spaces $\alpha_t, t\in\iota$ as global
variables.  In Lean, the product space is then \leanline{∀ j : ι, α j}
and the product over a finite subset \leanline{J} of \leanline{ι} is \leanline{∀ j : J, α
  j}.
